\documentclass[a4paper]{article}

\usepackage{appendix}
\usepackage{cleveref}
\usepackage{enumitem}
\usepackage[margin=2.5cm]{geometry}
\usepackage[utf8]{inputenc}

\newenvironment{enumsection}[1]{\section{#1} \begin{enumerate}[ref=\thesection.\theenumi]}{\end{enumerate}}

\title{Subcommittee Organisation and Management}
\author{Cameron Hall Interclub Operational Network}
\date{}

\begin{document}

\maketitle

\begin{enumsection}{Purpose of These Guidelines}
    \item These guidelines are meant to be approved by all relevant committees prior to the formation of any subcommittees.
    \item These guidelines are intended to clearly identify the duties of individuals and the subcommittee, and to allow for straightforward dispute resolution int he case of disagreements.
    \item These guidelines are intended to be put in place for the duration of a club's committee term, with subcommittees to be formed based on the regulations already in place.
\end{enumsection}

\begin{enumsection}{Alterations to This Document}
    \item These regulations may be modified for a specific event by a simple majority vote of:
    \begin{enumerate}
        \item The subcommittee of the event; and
        \item The committee of each club participating in the event.
    \end{enumerate}
\end{enumsection}

\begin{enumsection}{Subcommittee Composition}
    \item An event committee should be formed by an equal number of committee members from each club that is involved in running the event.
    \begin{enumerate}
        \item The number of committee members each club should send shall be agreed upon by the clubs involved prior to the formation of the subcommittee.
        \item A club may choose to send fewer committee members with the understanding that this will affect their voting power on the committee.
        \item Each club's committee shall be responsible for communicating their representatives to other clubs involved in the event.
    \end{enumerate}
    \item The event committee will be in charge of organising and running the event with the approval of the involved clubs.
    \item Each club shall nominate unique representatives, that is, no subcommittee member may represent more than one club.
    \item The subcommittee shall dissolve subsequent to the conclusion of the event, division of profits, and release of financial statement.
    \item A club may replace a representative upon consultation with the subcommittee.
\end{enumsection}

\begin{enumsection}{Subcommittee's Duties}
    \item It is the duty of the event subcommittee to:
    \begin{enumerate}
        \item Meet at least twice prior to the event;
        \item Meet at least once subsequent to the event;
        \item Elect one member to chair the meetings;
        \item Elect one member to distribute an agenda and minute the meetings;
        \begin{enumerate}
            \item All subcommittee members shall be able to add items to the agenda.
            \item All minutes must be made available to the committees of the clubs involved in the event in a timely manner.
        \end{enumerate}
        \item Elect one member to track action items and deadlines;
        \item Prepare an event budget prior to the event;
        \item Prepare a financial statement subsequent to the event; and
        \item Inform any club if their representative is failing to adequately perform their duties, as specified, in a timely manner.
    \end{enumerate}
    \item All decisions made by the event subcommittee shall be recorded in writing.
\end{enumsection}

\begin{enumsection}{Subcommittee Meetings}
    \item Subcommittee meetings may be called by any member of the subcommittee.
    \begin{enumerate}
        \item Subcommittee members shall receive three days' notices of any such meeting.
    \end{enumerate}
    \item The quorum of a subcommittee meeting shall be one subcommittee member representing each club involved in the event.
    \begin{enumerate}
        \item In the event that all representatives of a club cannot attend a scheduled meeting, they may elect to send a proxy from their committee or to forfeit their attendance rights at the meeting with the understanding this may effect their voting power.
        \item Abstentions shall not be counted towards quorum.
    \end{enumerate}
    \item In the event that all of a club's representatives are absent without apologies the subcommittee may enact committee of the whole as defined by the UWA Guild Standing Orders.
    \begin{enumerate}
        \item The relevant club's committee shall be informed immediately.
    \end{enumerate}
\end{enumsection}

\begin{enumsection}{Individuals' Duties}
    \item It is the duty of each club representative to:
    \begin{enumerate}
        \item Represent their club and its views in all event committee meetings;
        \item Assist in the planning, organisation, set-up, running, clean-up, and resolution of the event;
        \item Keep their club's committee informed of all plans, outcomes, and potential issues regarding the event and the event committee;
        \item Consult their committee regarding all major decisions concerning the event (such as dates, prices, themes, and venues, or any matter that an event committee member requests approval for) prior to voting;
        \item Distribute an itemised budget to their committee for approval in a timely manner;
        \item Liaise between the club and event committee, bringing forward any suggestions or issues;
        \item Advertise and promote the event to the members of their club;
        \item Distribute all minutes to their committee in a timely manner; and
        \item Distribute an itemised financial statement to their committee in a timely manner.
    \end{enumerate}
\end{enumsection}

\begin{enumsection}{Finances}
    \item The subcommittee not having the power to distribute funds independently of their respective clubs, any finances required are to be sourced from the club(s) involved in the event.
    \begin{enumerate}
        \item All financial decisions and budgets shall be subject to review by the committee of any club in question.
    \end{enumerate}
    \item The subcommittee shall vote on the division of profits prior to the event.
    \begin{enumerate}
        \item If any club's representatives fail to adequately perform their duties as outlined in the above sections, the division of profits may be altered by a two-thirds majority vote.
    \end{enumerate}
    \item Costs shall be reimbursed from the event's income prior to distribution of profit.
    \begin{enumerate}
        \item Costs not included in the event budget or approved by the event subcommittee prior to purchase may be liable to not be refunded.
    \end{enumerate}
\end{enumsection}

\appendixpage

\appendix \section{History of this Document} \label{app:history}

\begin{itemize}
    \item[] Prepared by Sarah Lewis and Taylor Home 2016-04-10.
    \item[] Edited by Taylor Home 2017-03-17.
    \item[] Edited by Taylor Home 2018-08-07 based on 2018-04-10 consultation with:
    \begin{itemize}
        \item Andrew Gozzard, UCC President;
        \item Eim\'ile Humphreys, Pantomime Society President;
        \item Simon Lawrance, UniSFA President;
        \item Tze Wen "Lewis" Lee, UWAnime President; and
        \item Gavin Tay Fernandez, Unigames Presdient.
    \end{itemize}
\end{itemize}

\end{document}
